Sodium silicate and hexametaphosphate promote the release of (oxyhydr)oxide nanoparticles from corroding iron

### 2022-06-24 Rmarkdown/paper.Rmd
readme + eq correction

We estimated the radius of gyration ($r_g$) associated with each light scattering peak and fractogram using the Zimm model [@kammer_fieldflow_2005; @wyatt_light_1993; @baalousha_size_2006]. Specifically, we solved the following equation for $r_g^2$, the mean squared radius of gyration:

@@

$$\langle{r^2_g}\rangle = \frac{3\beta_1\lambda^2}{16\beta_0\pi^2}$$

>>>>

We estimated the radius of gyration ($r_g$) of iron nanoparticles in each suspension using the Zimm model [@kammer_fieldflow_2005; @wyatt_light_1993; @baalousha_size_2006; @petteys_characterization_1998]. Specifically, we solved the following equation for $r_g^2$, the mean squared radius of gyration:

@@

$$\langle{r^2_g}\rangle = \frac{3\beta_1\lambda^2}{16\beta_0\pi^2\eta_0^2}$$
